%!TEX root = ../thesis.tex
% створюємо список використаної літератури
\begin{thebibliography}
    \bibitem{1}
    Hopcroft J. E.; Ullman J. D. Introduction to Automata Theory, Languages, and Computation // Addison-Wesley. - 1979

    \bibitem{2}
    Lari K.; Young S. J. Applications of stochastic context-free grammars using the inside-outside algorithm // Computer Speech and Language. - 1991

    \bibitem{3}
    Lari K.; Young S. J. The estimation of stochastic context-free grammars using the inside-outside algorithm // Computer Speech and Language. - 1990

    \bibitem{4}
    Chomsky, Noam. Three models for the description of language. // IRE Transactions on Information Theory. - 1956

    \bibitem{5}
    Chomsky, Noam. On certain formal properties of grammars // Information and Control - 1959

    \bibitem{6}
    А. М. Яглом; И. М. Яглом. Вероятность и информация // Главное издательство физико-математической литературы, Москва - 1973

    \bibitem{7}
    Greibach, Sheila. A New Normal-Form Theorem for Context-Free Phrase Structure Grammars // Journal of the ACM. 12 - 1965

    \bibitem{8}
    Jurafsky, D.; Martin, J. H. Speech and language processing: An introduction to natural language processing, computational linguistics, and speech recognition // Upper Saddle River, N.J: Pearson Prentice Hall. - 2009

    \bibitem{9}
    Baum, L. E.; Petrie, T.; Soules, G.; Weiss, N. A Maximization Technique Occurring in the Statistical Analysis of Probabilistic Functions of Markov Chains // The Annals of Mathematical Statistics. 41 - 1970

    \bibitem{10}
    Baum, L. E.; Petrie, T. Statistical Inference for Probabilistic Functions of Finite State Markov Chains // The Annals of Mathematical Statistics. 37 - 1966

    \bibitem{11}
    Sakakibara, Y., Brown, M., Hughley, R., Mian, I., Sjolander, K., Underwood, R., Haussler, D.: Stochastic context-free grammars for tRNA modeling. // Nuclear Acids Res. 22 - 1994

    \bibitem{12}
    From hidden markov models to stochastic contex-free grammars // Statistics 246, week 9b, spring 2002[Електронний ресурс] Режим доступу --- \url{http://www.stat.berkeley.edu/~terry/Classes/s246.2002/Week9/week9b.pdf}

    \bibitem{13}
    Viterbi A. J. Error bounds for convolutional codes and an asymptotically optimum decoding algorithm // IEEE Transactions on Information Theory. 13 (2) - 1967

    \bibitem{14}
    Eddy S. R.; Durbin R. RNA sequence analysis using covariance models. // Nucleic Acids Research. 22 (11) - 1994

    \bibitem{15}
    Xiaolin Li, Marc Parizeau, Réjean Plamondon: Training Hidden Markov Models with Multiple Observations – A Combinatorial Method // IEEE Transactions on PAMI, vol. PAMI-22, no. 4, pp 371-377 - 2000

    \bibitem{16}
    Robert Koch, Norbert Blum: Greibach Normal Form Transformation, Revisited // Information and Computation Volume 150, Issue 1 - 1999

    \bibitem{17}
    Andrzej Ehrenfeucht, Grzegorz Rozenberg: An Easy Proof of Greibach Normal Form // Information And Control 63, 190-199 - 1984

    \bibitem{18}
    Репозиторій на GitHub[Електронний ресурс] Режим доступу --- \url{https://github.com/juja256/hmm2s}

    \bibitem{19}
    Uanhua Lv, ChengXiang Zhai: Positional Language Models for Information Retrieval // SIGIR’09 - 2009

    \bibitem{20}
    Ravi Ganesan, Alan T. Sherman: Statistical Techniques for Language Recognition: An Introduction And Guide for Cryptanalysis - 1993

    \bibitem{21}
    Tomas Mikolov, Kai Chen, Greg Corrado, Jeffrey Dean: Efficient Estimation of Word Representations in Vector Space - 2013 // Режим доступу --- \url{https://arxiv.org/pdf/1301.3781.pdf}

    \bibitem{22}
    Paul Ibbotson, Michael Tomasello: Evidence Rebuts Chomsky's Theory of Language Learning // Scientific American - 2016
\end{thebibliography}
